---
title: "Jaz TidyTuesday Doctor Who week"
---

# Dr. Who - what years were the most popular episodes aired?

The data this week comes from [datardis package by way of Jonathan Kit]

Credit: [Jasmine Wilson](Twitter:%20@Wilson_Jaz)

### Library

```{r}
#Load library
pacman::p_load(dplyr, inspectdf, visdat, readr, tidyverse, DataExplorer, tidyr, plyr,epiDisplay, showtext, ggplot2,plotly, LaCroixColoR, gridExtra, ggrepel, plotly, ggtext, png)

font_add_google("Orbitron", "orbitron")
showtext_opts(dpi = 320)
showtext_auto()

```

### Read in data

```{r}
directors <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-11-23/directors.csv')
episodes <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-11-23/episodes.csv')
writers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-11-23/writers.csv')
imdb <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-11-23/imdb.csv')

imdb_rn <- imdb %>% dplyr::rename(rating_imdb = rating)

```

### join data tables
```{r}
dir_ep <- full_join(
  directors,
  episodes,
  by = "story_number",
  copy = FALSE
)

dir_ep_wri <-  full_join(
  dir_ep,
  writers,
  by = "story_number",
  copy = FALSE
)

data_all <-  full_join(
  dir_ep_wri,
  imdb_rn,
  by =c("season_number" = "season", "episode_number" = "ep_num" )
)

#Drop col
data_all2 <- subset( data_all, select = -c(serial_title, production_code) ) # WILL
head(data_all2)

#Drop NA
df <- na.omit(data_all2)

#split air date into d/m/y
df <- df %>% separate(air_date, c("air_day", "air_month", "air_year"))

#change rating to numeric
as.numeric(df$rating_imdb)
class(df$rating_imdb)

```

### inspect data 

```{r}
inspect_types(df)  %>% show_plot()
inspect_num(df)    %>% show_plot()
inspect_imb(df) %>% show_plot()
inspect_cat(df) %>% show_plot()
inspect_cor(df) %>% show_plot()

library(DataExplorer)
DataExplorer::create_report(df)
```

### plot data 

```{r}

p <- df %>%
  mutate(text = paste( "Duration(min): ", duration, 
                       "\nImdb_rating: ", rating_imdb, 
                       "\nUK_viewers (mn): ", uk_viewers, 
                       sep="")) %>%
  ggplot(aes(x=uk_viewers, y=rating_imdb, size = duration, color = air_year, text = text)) +
      geom_point(alpha=0.8) +
      scale_size(range = c(1, 15), name="Episode duration (min)") +
      scale_color_manual(values=lacroix_palette("PeachPear",type = "continuous", n=12)) +
      guides(size = guide_legend(override.aes = list(color = "white"))) +
  
     labs(
     title = "Doctor Who: Best episodes in the past?", 
     y = "Imdb ratings (1-10)", 
     x = "Number of UK viewers (millions)", 
     #subtitle = "Vinsert words here", 
     caption = "@Wilson_Jaz| source = {datardis} R package") + 

  theme(plot.background  = element_rect(fill= "#000e29",),
        plot.margin      = margin(10, 15, 10, 20),
        panel.background = element_rect(fill = NA, colour = NA),
        panel.border     = element_rect(fill = NA, colour = NA),
        panel.grid.major.y = element_line(colour = "#7c7e81", linetype = "dotted"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
       
        axis.text.x  = element_text(size = 10, colour = "#7c7e81"),
        axis.text.y  = element_text(size = 10, colour = "#7c7e81"),
        axis.ticks   = element_blank(),
        axis.title.y = element_text(size = 12,  margin = margin(r = 10)),
        axis.title.x = element_text(size = 12,  margin = margin(b = -10)),
        
        plot.caption = element_text(family = "orbitron", size = 8,colour = "grey70"),
        plot.caption.position = "plot",
        
        legend.background = element_rect(fill = "#000e29", color="#000e29", size=2),
        legend.box.background = element_rect(fill = "#000e29", color="#000e29", size=2),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key=element_blank(),
        legend.direction = "vertical", 
        legend.position = "right",
        legend.box = "horizontal",
        legend.key.height=unit(1,"line"),
        
  
        #legend.key = element_blank(),
        #legend.key.width = unit(2, "lines"),
        
        plot.title = element_text(colour = "white",
                                  family = "orbitron",
                                  size = 20,
                                  #margin = margin(0, 0, 45, 0)
                                  ),
        plot.subtitle = element_text(colour = "#afd0dc",
                                   family = "orbitron",
                                   size = 15,
                                   #margin = margin(10, 0, 10, 0)
                                   ),
        legend.text = element_text(colour = "#afd0dc",
                                   family = "orbitron",
                                   size = 10),
        legend.title = element_text(colour = "white",
                                    family = "orbitron",
                                    size = 10),
        axis.title = element_text(colour = "#b1c6ef",
                                  family = "orbitron",
                                  size = 6),
        axis.text = element_text(colour = "#7e7b7b",
                                 family = "orbitron"))
view(p)

#Save plot 
ggsave(p, file = "filepath/plot.png", width=30, height =20, units = "cm")
    
#for interactive plot 
ggplotly(p, tooltip="text")

#save interactive plot 
ip <- ggplotly(p, tooltip="text")
htmlwidgets::saveWidget(ip, "~/Desktop/plot.html")
```

#notes - imdb rating scale:

1 Ridiculous (Burn) 
2 Awful (Nobody can you cant borrow it)) 
3 Bad (No but you can borrow it)\
4 ehh (No desire to watch again might with someone)\
5 Average (Probably not)\
6 Good (Maybe) 7 Good + (Probably)\
8 Very Good (Again)\
9 Excellent (Again and Again)\
10 Amazing (Indeffinitely)