---
title: "Tidy Tuesday Week 2: Transit Cost Project"
output: html_notebook
---

# Transit Cost Project

**The data this week comes from [Transit Costs Project](https://transitcosts.com).**

*The [Transit Costs Project](https://transitcosts.com) talks about compares the costs of transit projects worldwide in greater detail.*

**Credit**: [Dr Jasmine Wilson](@WilsonJasmine)

## Read in data

```{r}
library(tidyverse)
library(rgdal) 
library(rgeos) 
library(tidyselect) 
library(tmap) 
library(leaflet) 
library(RJSONIO) 
library(sf) 
library(tmap)
library(ggplot2)
library(cowplot)
```

## Read in data and filter out NA values

```{r}
transit_cost <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-05/transit_cost.csv')

## Filtering out rows with missing values

# list rows of data which have missing values 
transit_cost[!complete.cases(transit_cost),]
# create new dataset without missing data 
TC <- na.omit(transit_cost)
```

## Calculate total length of time taken or estimated for each project

```{r}

class(TC$start_year)
class(TC$end_year)

#Change the class to an integer
TC$start_year_num = as.integer(TC$start_year)
TC$end_year_num   = as.integer(TC$end_year)

#Check to see NA rows 
TC[!complete.cases(TC),]
#only one row - end year = x

# create new data set without missing data 
TC_1 <- na.omit(TC)

#Adding new column for total time taken for project
TC_1 <- 
       mutate(TC_1 
       , total_years = end_year_num - start_year_num
       , length_per_year = (length/total_years))

```


## Add latitude and longitude for spatial mapping of data


```{r}

# To add associated lat/lon: <https://stackoverflow.com/questions/13905098/how-to-get-the-longitude-and-latitude-coordinates-from-a-city-name-and-country-i>
# Use: library(RJSONIO)

nrow <- nrow(TC_1)
counter <- 1
TC_1$lon[counter] <- 0
TC_1$lat[counter] <- 0
while (counter <= nrow){
  CityName <- gsub(' ','%20',TC_1$city[counter]) 
  CountryCode <- TC_1$country[counter]
  url <- paste(
    "http://nominatim.openstreetmap.org/search?city="
    , CityName
    , "&countrycodes="
    , CountryCode
    , "&limit=9&format=json"
    , sep="")
  x <- fromJSON(url)
  if(is.vector(x)){
    TC_1$lon[counter] <- x[[1]]$lon
    TC_1$lat[counter] <- x[[1]]$lat    
  }
  counter <- counter + 1
}

```


Convert data to spatial format and plot map points

```{r}

#Convert lat and lon to numeric
TC_1$lat.num <- as.numeric(TC_1$lat)
TC_1$lon.num <- as.numeric(TC_1$lon)

#Convert data to spatial format
#We will be using the standard EPSG:4326 or WGS 84 projection 
#Use: library(sf)

map.points = st_as_sf(TC_1
                      , coords = c("lon.num", "lat.num")
                      , crs = 4326
                      , agr = "constant")

class(map.points)

##Plot map points
#Use: library(tmap)

head(map.points)

tmap_mode('view') #"view" = interactive, "plot" = non-interactive

tmap_options(bg.color = "black", legend.text.color = "white")


Map_Plot_1 =    tm_shape(map.points) +
                tm_dots(col ="total_years"
                , size  = 0.1
                , style = "pretty"
                , id    = "city"
                , popup.vars = c(
                "city:" = "city", 
                "country:" = "country") # light in popup
                , breaks = c(0,1,2,Inf)
                , palette = c("aquamarine2", "cornflowerblue", "brown1")
                , title = "Project length in years") +
                  tm_layout("Long lat coordinates (WGS84)", inner.margins=c(0,0,.1,0), title.size=.8) +
                  tm_basemap("Stamen.Watercolor")
Map_Plot_1


Map_Plot_2 =    tm_shape(map.points) +
                tm_dots(col ="cost"
                , size  = 0.1
                , style = "pretty"
                , id    = "city"
                , popup.vars = c(
                "city:" = "city", 
                "country:" = "country") # light in popup
                , breaks = c(0,1,2,Inf)
                , palette = c("aquamarine2", "cornflowerblue", "brown1")
                , title = "Cost of project (millions)") +
                  tm_layout("Long lat coordinates (WGS84)", inner.margins=c(0,0,.1,0), title.size=.8) +
                  tm_basemap("Stamen.Watercolor")

Map_Plot_2

#View multiple variables cocurrently
Facets = tm_shape(map.points) +
    tm_dots(c("total_years", "cost")) +
    tm_facets(sync = TRUE, ncol = 2)
Facets      

## save an image ("plot" mode)
tmap_save(Map_Plot_1, filename = "Project length in years.html")

## save as stand-alone HTML file ("view" mode)
tmap_save(Map_Plot_2, filename = "Cost project.html")


```

#make RShiny app

```{r}

data(map.points)
map.points.select <- 	select(map.points, country, city, start_year, end_year, length, cost, real_cost, ppp_rate, cost_km_millions, currency, total_years, length_per_year)

world_vars <- setdiff(names(map.points.select), c("iso_a3", "start_year", "length", "cost"))
	

	
	ui <- fluidPage(
		    titlePanel("Data Transit costs"),
		    tmapOutput("map"),
	    	selectInput("var", "Variable", 
		            c("Length (Km)"             = "length",
                  "Total years of project"  = "total_years",
		              "PPP rate"                = "ppp_rate",
		              "Cost Millions per KM"    = "cost_km_millions",
		              "unit length per year"    = "length_per_year"))
	)
	
	server <- function(input, output, session) {
		output$map <- renderTmap({
			tm_shape(map.points) +
				  tm_dots(col = world_vars[1], zindex = 401)
		})
		
		observe({
			var <- input$var
			tmapProxy("map", session, {
				tm_remove_layer(401) +
				tm_shape(map.points) +
					tm_dots(var
					      , zindex = 401
					      , size  = 0.05
                , style = "pretty"
                , id    = "city"
                , popup.vars = c(
                                  "city:" = "city", 
                                  "country:" = "country") # light in popup
                , breaks = c(0,1,2,Inf)
                , palette = c("aquamarine2", "cornflowerblue", "brown1")
                , title = "Legendary") +
        
			    tm_layout("Long lat coordinates (WGS84)"
                , inner.margins=c(0,0,.1,0)
                , title.size=.8)
			})
		})
	}	
	
	
	app <- shinyApp(ui, server)
	if (interactive()) app
	

```

Plot relationships
```{r}
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(plotly)
library(d3heatmap)

# Load data 

data_3 <- TC_1 %>% as.data.frame()

# Select a few country
Country_selected = subset(data_3, country %in% c( "IN","RU", "MX","DK", "NO", "AU", "SG" ))

p4 = ggplot(Country_selected
         , aes(x = length, y = cost)) +
           geom_point(size = 2, shape = 21, stroke = 1, (aes(color = country))) +
           labs(x = "Cost (millions)"
              , y = "Length of transit project"
              , subtitle = "Cost and length of transit project") 

p4

p5 = ggplot(Country_selected
           , aes(x = length, y = cost))+
    geom_point (aes(color = country)) +
    geom_smooth(aes(color = country, fill = country), method = "lm") + 
    scale_color_viridis(discrete = TRUE, option = "B")+
    scale_fill_viridis(discrete = TRUE)+
    xlab("cost") +
    ylab("Length of transit line (km)")
p5


ggsave(p4, filename = "Cost v length of transit project")
```


# Heatmap 

```{r}
library(tidyverse)
library(hrbrthemes)
library(kableExtra)
options(knitr.table.format = "html")
library(patchwork)

data = TC_1

# Plot
p6 = (Country_selected %>%
     filter(!is.na(total_years)) %>%
     arrange(total_years) %>%
     ggplot( aes(x=country, y=total_years) ) +
     geom_segment( aes(x=country ,xend=country, y=0, yend=total_years), color="grey") +
     geom_point(size=3, color="#69b3a2") +
     coord_flip() +
     theme_ipsum() +
     theme(
       panel.grid.minor.y = element_blank(),
       panel.grid.major.y = element_blank(),
       legend.position="none"
    ) +
    xlab("") +
    ylab("Length of project (years)"))
```



```{r}



```

